MISUSES AND INACCURACIES OF PAGEL'S LAMBDA ML ESTIMATION METHODS

### 2020-03-24 Manuscript-template.rmd
Organizing data, running fixed simulation scripts for Regressions analyses. Not yet finished: reg tree size 512 and 1028, and all ANOVA analyses.

Rensch's rule, the allometric association between the degree of sexual dimorphism and overall body size, is an important framework for understanding the evolution of trends in phenotypic differentiation between the sexes across taxa. While virtually all recent treatments have explored the degree of sexual size dimorphism, understanding how dimorphism in other phenotypic traits evolves is equally relevant. Indeed, Rensch's original treatment focused not only on size, but also on dimorphism in relative body proportions, coloration, the presence of ornaments, etc. Here, we derive a multivariate equivalency for viewing trends in sexual dimorphism – relative to overall body size – across taxa, and provide a generalized test to determine whether such patterns are consistent with Rensch's rule. For univariate linear traits such as body size, our approach yields equivalent results to those from standard procedures, but our test is also capable of detecting trends in multivariate datasets like shape. Computer simulations reveal the method displays appropriate statistical properties, and an empirical example in Mediterranean lizards illustrates the efficacy of our approach on both univariate and multivariate phenotypes. Our generalized procedure substantially extends the toolkit available for investigating macroevolutionary patterns of sexual dimorphism and seeking a better understanding of the processes that underlie them.

>>>>

Rensch's rule, the allometric association between the degree of sexual dimorphism and overall body size, is an important framework for understanding the evolution of trends in phenotypic differentiation between the sexes across taxa. While virtually all recent treatments have explored the degree of sexual size dimorphism, understanding how dimorphism in other phenotypic traits evolves is equally relevant. Indeed, Rensch's original treatment focused not only on size, but also on dimorphism in relative body proportions, coloration, the presence of ornaments, etc. <!-- I think this can be rephrased --> Here, we derive a multivariate equivalency for viewing trends in sexual dimorphism – relative to overall body size – across taxa, and provide a generalized test to determine whether such patterns are consistent with Rensch's rule. For univariate linear traits such as body size, our approach yields equivalent results to those from standard procedures, but our test is also capable of detecting trends in multivariate datasets like shape. Computer simulations reveal the method displays appropriate statistical properties, and an empirical example in Mediterranean lizards illustrates the efficacy of our approach on both univariate and multivariate phenotypes. Our generalized procedure substantially extends the toolkit available for investigating macroevolutionary patterns of sexual dimorphism and seeking a better understanding of the processes that underlie them.
